Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2022-03-14 paper/introduction.tex
Small writing changes in first two sections.

In this work, we develop \textcolor{red}{a family of empirical surrogate models} for the tritium breeding
ratio (TBR) in an inertial confinement fusion (ICF) reactor. The expensive model
that our surrogate model approximates is a Monte Carlo (MC) neutronics
simulation, Paramak~\cite{paramak}, which returns a prediction of the TBR for a given
configuration of a spherical ICF reactor. Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods. \textcolor{red}{We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.}

@@

Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
a portable Docker container, which conveniently exposes an HTTP API using the
Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
geometry was deliberately left adjustable, so that dependency of TBR on various
parameters may be explored. Nuclear data for simulation was extracted from the following sources, in order of preference: \textcolor{red}{FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}}.
To maintain model-agnostic approach, variance reduction (VR) techniques
were not used to accelerate the MC neutronics simulation~\cite{Kleijnen2013}.
It should be noted that depending on application, VR may constitute a viable
alternative to the presented work.

For the remainder of~\Sref{sec:introduction}, we will define the TBR and further motivate our
research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
testing of a wide variety of surrogate modelling techniques, as well as defining the adaptive sampling procedure QASS. After delivering the
results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
recommendations in~\Sref{sec:conclusion}.

\footnotetext[1]{A bug in the Muir distribution involving erronous normal
sampling was recently uncovered (see
\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present approach-focused work.}

@@

Nuclear fusion technology relies on the production and containment of an
extremely hot and dense plasma containing enriched Hydrogen isotopes. The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
under-construction \textcolor{red}{ITER}, make
use of both tritium and deuterium fuel. While at least one deuterium atom occurs for every \num{5000} molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature. It may be produced indirectly through irradiation of heavy water
(\DDO) during nuclear fission, but only at very low rates which could
never sustain industrial-scale fusion power.

\textcolor{red}{Modern} D-T reactors rely on tritium breeding blankets, specialized
layers of material which partially line the reactor and produce tritium upon
neutron bombardment, e.g.~by 
\begin{eqnarray}
	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt}\isotope[4][2]{He} \\
	\isotope[1][0]{n} + \hspace{3pt} \isotope[7][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
\end{eqnarray}%
where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. \textcolor{red}{The TBR is defined as the ratio of tritium produced per source neutron}
, whose description in Paramak is facilitated by 2~classes of parameters
(exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
reactor is described by continuous parameters, material selections are specified
by discrete categorical parameters. For all parameters, we have attempted to cover the full theoretical range of values even where those values are practically infeasible with current technology (e.g. packing fractions close to 1). Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.

In our work, we set out to produce a \textcolor{red}{fast TBR surrogate model}, which takes the same input parameters \textcolor{red}{as the MC model used in Paramak and approximates its output} with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples \textcolor{red}{needed for training}.

>>>>

In this work, we develop \textcolor{red}{a family of empirical surrogate models} for the tritium breeding
ratio (TBR) in an inertial confinement fusion (ICF) reactor. The expensive model
that our surrogate model approximates is a Monte Carlo (MC) neutronics
simulation, Paramak~\cite{paramak}, which returns a prediction of the TBR for a given
configuration of a spherical ICF reactor. Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods. \textcolor{red}{We quantify the success of several of our best-performing surrogate models by studying their accuracy and prediction time. We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.}

@@

Paramak facilitates simulation via \textcolor{red}{an} OpenMC neutronics workflow that is enclosed in
a portable Docker container, which conveniently exposes an HTTP API using the
Python~3 \texttt{flask} package. \textcolor{red}{Within this setup, we employ} a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated \textcolor{red}{reactor}
geometry was left adjustable \textcolor{red}{in order to study its influence on the TBR}. Nuclear data for simulation was extracted from the following sources, in order of preference: \textcolor{red}{FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}}.
To maintain model-agnostic approach, variance reduction (VR) techniques
were not used to accelerate the MC neutronics simulation~\cite{Kleijnen2013}.
It should be noted that depending on application, VR may constitute a viable
alternative to the presented work.

For the remainder of~\Sref{sec:introduction}, we will define the TBR and further motivate our
research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
testing of a wide variety of surrogate modelling techniques, as well as defining \textcolor{red}{an add-on} adaptive sampling procedure QASS. After delivering the
results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
recommendations in~\Sref{sec:conclusion}.

\footnotetext[1]{A bug in the Muir distribution involving erronous normal
sampling was recently uncovered (see
\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present \textcolor{red}{methods-focused} work.}

@@

Nuclear fusion technology relies on the production and containment of an
extremely hot and dense plasma containing enriched Hydrogen isotopes. The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
under-construction \textcolor{red}{ITER}, make
use of both tritium and deuterium fuel. While at least one deuterium atom occurs for every \num{5000} molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature. \textcolor{red}{Tritium} may be produced indirectly through irradiation of heavy water
(\DDO) during nuclear fission, but only at very low rates which could
never sustain industrial-scale fusion power.

\textcolor{red}{Modern} D-T reactors rely on tritium breeding blankets, specialized
layers of material which partially line the reactor and produce tritium upon
neutron bombardment, e.g.~by 
\begin{eqnarray}
	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt}\isotope[4][2]{He} \\
	\isotope[1][0]{n} + \hspace{3pt} \isotope[7][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}.
\end{eqnarray}%
%
\textcolor{red}{The TBR is defined as the ratio of tritium produced per source neutron}, whose description in Paramak is facilitated by \textcolor{red}{two} classes of parameters
(exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
reactor is described by continuous parameters, material selections are specified
by discrete categorical parameters. For all parameters, we have attempted to cover the full theoretical range of values even where those values are practically infeasible with current technology (e.g. packing fractions close to 1). Simulating broadly around typical values of parameters \textcolor{red}{improves the accuracy of the model nearer to typical values}, and also aids in demonstrating the robustness of constructed models.

In our work, we set out to produce a \textcolor{red}{fast TBR surrogate model}, which takes the same input parameters \textcolor{red}{as the MC model used in Paramak and approximates its output} with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples \textcolor{red}{needed for training}. \textcolor{red}{This represents a significant step forwards in computational fusion-reactor design, as any speed-up achieved in TBR evaluation directly informs a speed-up in numerical optimization of reactor parameters, although such optimization is beyond the scope of the present work.}

### 2022-03-14 paper/methodology.tex
Small writing changes in first two sections.

Labeling the expensive Paramak model $f(x)$, a surrogate is a mapping
$\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimize a selected dissimilarity
metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
achieve expected evaluation time lower than that of~$f(x)$. In this work, we
consider 2~methods of producing viable surrogates: (1)~a conventional decoupled
approach, which evaluates $f(x)$ on a set of randomly sampled points and
trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
compensate for localized regression performance insufficiency's by interleaving
multiple epochs of sampling and training.

@@

\begin{table*}[t]
	\renewcommand{\arraystretch}{0.95}
	\caption{\label{tbl:metrics}Metrics recorded in experiments. In
	formulations, we work with a training set of size $N_0$ and a test set of
size $N$, values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in Paramak and the surrogate
respectively. The mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
number of input features.}
	\begin{indented}
	\item[]
		\begin{tabularx}{\textwidth}{Xrl}
		\toprule
		Regression performance metrics& Notation	& Mathematical formulation\\
		\midrule
		Mean absolute error	& MAE & $N^{-1}\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|$ \\
		Standard deviation of error & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $ \\
			Coefficient of determination & $R^2$	& $1-\sum_{i=1}^N
			\left(y^{(i)}-\hat{y}^{(i)} \right)^2\left[\sum_{i=1}^N \left(
			y^{(i)}-\overline{y} \right)^2\right]^{-1} $ \\
			Adjusted $R^2$ & $R^2_\text{adj.}$	& $1-(1-R^2)(N-1)(N-P-1)^{-1}$ \\
		\midrule
		Computational complexity metrics	& {}	& {} \\
		\midrule
		Mean training time & $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})N_0^{-1}$  \\
			Mean prediction time & $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
			$\hat{f}(x)$})N^{-1}$ \\
				Relative speedup & $\omega$	& $(\text{wall evaluation$^\text{b}$ time of $f(x)$})
				(N\overline{t}_{\text{pred.}})^{-1}$ \\
		\bottomrule
		\end{tabularx}\\%
		{\footnotesize $^\text{b}$This corresponds to evaluation of Paramak
		 on all points of the test set. In surrogates, the equivalent
		time period is referred to as ``prediction time.''}
	\end{indented}
\end{table*}

For both methods, we selected state-of-the-art regression algorithms to perform
surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
We note that each presented algorithm defines hyperparameters that may influence its
performance. Their problem-specific optimal values are searched within the scope
of this work, in particular in Experiments~1 \&~2 that are outlined
in~\Sref{sec:experiment-methodology}.

To compare the quality of the produced surrogates, we define a number of metrics listed
in~\Tref{tbl:metrics}. For regression performance analysis, we include a
selection of absolute metrics \textcolor{red}{(MAE, $S$)} to assess the models' approximation capability
and set practical bounds on the expected uncertainty of their predictions. In addition, we also track
relative measures \textcolor{red}{($R^2$, $R^2_\text{adj.}$)} that are better-suited for comparison between this work and others as
they are invariant with respect to the selected domain and image space.
For analysis of computational complexity, surrogates are assessed in terms of wall
time (captured by the Python~3 \texttt{time} package). This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for
Paramak. All times reported (training, test, evaluation) are
normalized by the corresponding dataset size, i.e.~correspond to ``time to
process a single datapoint.''

Even though some surrogates support acceleration by means of \textcolor{red}{parallelization}, we
used non-parallelized implementations. The only exception to this \textcolor{red}{is the ANN family},
which \textcolor{red}{requires} a considerable amount of processing power for training on
conventional CPU architectures. Lastly, to prevent undesirable bias by training
set selection, all reported metrics are obtained via 5-fold cross-validation.
In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
is used as a test set for models trained on the remaining 4. Having repeated the
same experiment for each division, the overall value of individual metrics is
reported in terms of their mean and standard deviation over all folds.

@@

Experiments related to the decoupled approach are organized in 4~parts,
further described in this section. In summary, we aim to optimize the hyperparameters of
each surrogate family separately and later use the best found results to compare surrogate
families among themselves.

The objective of Experiment~1 is to simplify the regression task for
surrogates prone to suboptimal performance in discontinuous spaces.
To this end, training points are filtered to a single selected discrete feature
assignment, and surrogates are trained only on the remaining continuous features.
This is repeated several times to explore variances in behaviour,
particularly in 4~distinct assignments that are obtained by setting blanket and
first wall coolant materials to one
of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.
Experiment~2 conventionally measures surrogate performance on the full feature
space without any parameter restrictions. In both experiments, hyperparameter tuning is
facilitated by Bayesian optimisation~\cite{movckus1975bayesian}, where we select the
hyperparameter configuration that produces the model that maximizes $R^2$. The
process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
The results of Experiments~1 \&~2 are depicted
in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
respectively, and described in~\Sref{sec:res-exp12}.

In Experiment~3, the 20~best-performing hyperparameter configurations
\textcolor{red}{for} each model family are used to train surrogates on sets of various sizes to
investigate their scaling properties. In particular, we track the metrics
from~\Tref{tbl:metrics} as functions of training set size (1, 2, 5, 10, 12, 15 and 20 thousands
of samples) individually for each family. This allows their comparison based on
observed trends, and estimation of optimal training set sizes.
The results of this experiment are shown in~\Fref{fig:scaling} and discussed
in~\Sref{sec:res-exp3}.

Finally, Experiment~4 aims
to produce surrogates suitable for practical use by retraining selected
well-scaling instances on large training sets in order to satisfy the goals of this work.
The results of this process are displayed in~\Fref{fig:reg-performance} and
in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}.

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \Fref{fig:qassplan}) to iteratively increment the training/test set with sample
points which maximize surrogate error and minimize a crowding distance metric
(CDM)~\cite{Solonen2012} in feature space. \textcolor{red}{Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.} On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.

>>>>

Labeling the expensive Paramak model $f(x)$, a surrogate \textcolor{red}{model is a function}
$\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimize a selected dissimilarity
metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
achieve \textcolor{red}{an} expected evaluation time lower than that of~$f(x)$. In this work, we
consider \textcolor{red}{two} methods of producing viable surrogates: (1)~a conventional decoupled
approach, which evaluates $f(x)$ on a set of \textcolor{red}{uniformly-random samples} and
trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
compensate for localized regression performance \textcolor{red}{insufficiencies} by interleaving
multiple epochs of sampling and training. \textcolor{red}{Several high-accuracy and deployment-ready surrogate models are developed using the decoupled approach, and their performance characterized numerically, while the adaptive approach is studied as a proof-of-concept.}

@@

\begin{table*}[t]
	\renewcommand{\arraystretch}{0.95}
	\caption{\label{tbl:metrics}Metrics recorded in experiments. In
	formulations, we work with a training set of size $N_0$ and a test set of
size $N$, values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in Paramak and the surrogate
respectively. The mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
number of input features.}
	\begin{indented}
	\item[]
		\begin{tabularx}{\textwidth}{Xrl}
		\toprule
		Regression performance metrics& Notation	& Mathematical formulation\\
		\midrule
		Mean absolute error	& MAE & $N^{-1}\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|$ \\
		Standard deviation of error & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $ \\
			Coefficient of determination & $R^2$	& $1-\sum_{i=1}^N
			\left(y^{(i)}-\hat{y}^{(i)} \right)^2\left[\sum_{i=1}^N \left(
			y^{(i)}-\overline{y} \right)^2\right]^{-1} $ \\
			Adjusted $R^2$ & $R^2_\text{adj.}$	& $1-(1-R^2)(N-1)(N-P-1)^{-1}$ \\
		\midrule
		Computational complexity metrics	& {}	& {} \\
		\midrule
		Mean training time & $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})N_0^{-1}$  \\
			Mean prediction time & $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
			$\hat{f}(x)$})N^{-1}$ \\
				Relative speedup & $\omega$	& $(\text{wall evaluation$^\text{b}$ time of $f(x)$})
				(N\overline{t}_{\text{pred.}})^{-1}$ \\
		\bottomrule
		\end{tabularx}\\%
		{\footnotesize $^\text{b}$This corresponds to evaluation of Paramak
		 on all points of the test set. In surrogates, the equivalent
		time period is referred to as \textcolor{red}{the} ``prediction time.''}
	\end{indented}
\end{table*}

We selected several state-of-the-art regression algorithms to perform
surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
implementations define \textcolor{red}{nine} surrogate families \textcolor{red}{which are detailed} in~\Sref{sec:results}.
We note that each presented algorithm defines hyperparameters that may influence its
performance. Their problem-specific optimal values are searched within the scope
of this work, in particular in Experiments~1 \&~2 that are outlined
in~\Sref{sec:experiment-methodology}.

To compare the quality of the produced surrogates, we define a \textcolor{red}{variety} of metrics listed
in~\Tref{tbl:metrics}. For regression performance analysis, we include a
selection of absolute metrics \textcolor{red}{(MAE, $S$)} to assess the models' approximation capability
and set practical bounds on the expected uncertainty of their predictions. In addition, we also track
relative measures \textcolor{red}{($R^2$, $R^2_\text{adj.}$)} that are better-suited for comparison between this work and others as
they are invariant with respect to the selected domain and image space.
For analysis of computational complexity, surrogates are assessed in terms of wall
time (captured by the Python~3 \texttt{time} package). This is motivated by common practical \textcolor{red}{use-cases} of our work, where surrogate models are trained as replacements for
Paramak. All times reported (training, test, evaluation) are
normalized by the corresponding dataset size, i.e.~correspond to ``time to
process a single datapoint.''

Even though some surrogates support acceleration by means of \textcolor{red}{parallelization}, we
used non-parallelized implementations. The only exception to this \textcolor{red}{is the ANN family},
which \textcolor{red}{requires} a considerable amount of processing power for training on
conventional CPU architectures. Lastly, to prevent undesirable bias by training
set selection, all reported metrics are obtained via 5-fold cross-validation.
In this setting, a sample set is uniformly divided into \textcolor{red}{five} disjoint folds, each of which
is used as a test set for models trained on the remaining \textcolor{red}{four}. Having repeated the
same experiment for each division, the overall value of individual metrics is reported in terms of their mean and standard deviation over all folds.

@@

Experiments related to the decoupled approach are organized in \textcolor{red}{four} parts,
further described in this section. In summary, we aim to optimize the hyperparameters of
each surrogate family separately, \textcolor{red}{and later compare the best results between
families.}

The objective of Experiment~1 is to simplify the regression task for
surrogates prone to suboptimal performance in \textcolor{red}{discrete} spaces.
To this end, training points are filtered to a single selected discrete feature
assignment, and surrogates are trained only on the remaining continuous features.
This is repeated several times to explore variances in behavior,
particularly in \textcolor{red}{four} distinct assignments that are obtained by setting blanket and
first wall coolant materials to one
of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.
Experiment~2 conventionally measures surrogate performance on the full feature
space without any parameter restrictions. In both experiments, hyperparameter tuning is
facilitated by Bayesian optimisation~\cite{movckus1975bayesian}, where we select the
hyperparameter configuration that produces the model that maximizes $R^2$. The
process is terminated after 1000~iterations or \textcolor{red}{two} days, whichever condition is satisfied first.
The results of Experiments~1 \&~2 are depicted
in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
respectively, and described in~\Sref{sec:res-exp12}.

In Experiment~3, the \textcolor{red}{twenty} best-performing hyperparameter configurations
\textcolor{red}{for} each model family are used to train surrogates on sets of various sizes to
investigate their scaling properties. In particular, we track the metrics
from~\Tref{tbl:metrics} as functions of training set size (1, 2, 5, 10, 12, 15 and 20 thousands
of samples) individually \textcolor{red}{for} each family. This allows their comparison based on
observed trends, and estimation of optimal training set sizes.
The results of this experiment are shown in~\Fref{fig:scaling} and discussed
in~\Sref{sec:res-exp3}.

Finally, Experiment~4 aims
to produce surrogates suitable for practical use by retraining selected
well-scaling instances on large training sets\textcolor{red}{.}
The results of this process are displayed in~\Fref{fig:reg-performance} and
in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}.

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \Fref{fig:qassplan}) to iteratively increment the training/test set with sample
points which maximize surrogate error and minimize a crowding distance metric
(CDM)~\cite{Solonen2012} in feature space. \textcolor{red}{Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.} On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated. MCMC was then performed to sample the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.
